% -----------------------------------------------
% Template for ISMIR Papers
% 2019 version, based on previous ISMIR templates

% Requirements :
% * 6+n page length maximum
% * 4MB maximum file size
% * Copyright note must appear in the bottom left corner of first page
% * Clearer statement about citing own work in anonymized submission
% (see conference website for additional details)
% -----------------------------------------------

\documentclass{article}
\usepackage[T1]{fontenc} % add special characters (e.g., umlaute)
\usepackage[utf8]{inputenc} % set utf-8 as default input encoding
\usepackage{ismir,amsmath,cite,url}
\usepackage{graphicx}
\usepackage{color}
\usepackage{pgfplots}

%% cleveref MUST be the last import
\usepackage{cleveref}

% Optional: To use hyperref, uncomment the following.
% \usepackage[bookmarks=false,hidelinks]{hyperref}
% Mind the bookmarks=false option; bookmarks are incompatible with ismir.sty.

% Title.
% ------
\title{Fractal dimension for music similarity and patterns in symbolic music data}

% Note: Please do NOT use \thanks or a \footnote in any of the author markup

% Single address
% To use with only one author or several with the same address
% ---------------
%\oneauthor
% {Names should be omitted for double-blind reviewing}
% {Affiliations should be omitted for double-blind reviewing}

% Two addresses
% --------------
%\twoauthors
%  {First author} {School \\ Department}
%  {Second author} {Company \\ Address}

%% To make customize author list in Creative Common license, uncomment and customize the next line
%  \def\authorname{First Author, Second Author}


% Three addresses
% --------------
\threeauthors
  {First Author} {Affiliation1 \\ {\tt author1@ismir.edu}}
  {Second Author} {\bf Retain these fake authors in\\\bf submission to preserve the formatting}
  {Third Author} {Affiliation3 \\ {\tt author3@ismir.edu}}

%% To make customize author list in Creative Common license, uncomment and customize the next line
%  \def\authorname{First Author, Second Author, Third Author}

% Four or more addresses
% OR alternative format for large number of co-authors
% ------------
%\multauthor
%{First author$^1$ \hspace{1cm} Second author$^1$ \hspace{1cm} Third author$^2$} { \bfseries{Fourth author$^3$ \hspace{1cm} Fifth author$^2$ \hspace{1cm} Sixth author$^1$}\\
%  $^1$ Department of Computer Science, University , Country\\
%$^2$ International Laboratories, City, Country\\
%$^3$  Company, Address\\
%{\tt\small CorrespondenceAuthor@ismir.edu, PossibleOtherAuthor@ismir.edu}
%}
%\def\authorname{First author, Second author, Third author, Fourth author, Fifth author, Sixth author}


\sloppy % please retain sloppy command for improved formatting

\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
\newcommand{\alternative}[1]{{\color{ao(english)}{#1}}}
\begin{document}

%
\maketitle
%
\begin{abstract}
  Fractals are highly regular objects with repetitions at different scales.
  \alternative{(Alternative intro sentence, for a more cross-disciplinary audience in mathematics and complex system research?:
    In mathematics, a fractal is a geometric object which exhibits regularity through self-similarity --- the whole being repeated at different scales, resulting to similar parts of itself.) }
  This has a natural counterpart in music: musical patterns repeat at different granularities of time.
  The hierarchical structures in fractals and music offer a starting point to describing and detecting these varying repetitions. 
  In this paper, we explore this connection quantitatively by examining these hierarchies at different levels and computationally measure the fractal dimension in music.
  We apply our framework to compute the time series of the fractal dimensions in monophonic symbolic corpora and synthesised data.
  For these different corpora, the distance matrices of the fractal dimensions exhibit distinct differences, showing a potential means to measure music similarity. 
  We further substantiate the novelty and usefulness of the fractal dimension by reporting its low correlations with previously-studied features.
  Using our approach, we are able to obtain patterns exhibiting certain geometric properties by thresholding on the fractal dimensions, permitting the extraction of pattern candidates with the same or similar melodic contours.

\end{abstract}

\input{src/body.tex}

\bibliography{references}

\end{document} 
